Trends of downward SDR in Thessaloniki

### 2023-04-27 Article.Rmd
Commit 2023-04-27 21:17

```{r echo=F, include=F, cache=T}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!h'    )

```

@@

>>>>

```{r echo=F, include=T}
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!h'    )
library(pander)
```

@@

\footnotesize
```{r trendtable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)

pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp <- pp[grep("Global" ,pp$var), ]

pander(pp)
```
\normalsize
